\textls[-0]{\thetitle}

### 2023-03-24 metatheory2.tex
cover letter
tweak

% Deal with intuition
\noindentparagraph{Why $\TyTkg{\cdot}$?}

@@

The problem lies in that the type $\TyLkg{\lsig^A}$ above cannot be inhabited.
Suppose there is some $\lkg^A$ such that $\cdot \vdash \lkg^A : \TyLkg{\lsig^A}$.
Then it follows from the self-parameterization that projecting out the last field~$f$
has the typing
$\goodTerm{T_A : \cU, T_B: \cU}{\lkgproj{2}{\lkg^A}}{\El{T_A} \to \El{T_B}}$.
This typing means that there is a function of type
$\nTyPi{T_A}{\cU}{\nTyPi{T_B}{\cU}{\El{T_A}
\to \El{T_B}}}$, i.e., a function from an arbitrary type to another arbitrary
type. We can easily derive inconsistency from this function:
we can apply it to $\top$ and $\bot$ and get $\top \to \bot$.

>>>>

% Deal with intuition
\noindentparagraph{Why $\TyTkg{\lsig}$?}

@@

The problem lies in that the type $\TyLkg{\lsig^A}$ above cannot be inhabited.
Suppose there is some $\lkg^A$ such that $\cdot \vdash \lkg^A : \TyLkg{\lsig^A}$.
Then it follows from the self-parameterization that projecting out the last field~$f$
from $\lkg^A$ (notated as $\lkg^A.f$ for illustration) has the typing
$\goodTerm{T_A : \cU, T_B: \cU}{\lkg^A.f}{\El{T_A} \to \El{T_B}}$.
This typing means that there is a function of type
$\nTyPi{T_A}{\cU}{\nTyPi{T_B}{\cU}{\El{T_A}
\to \El{T_B}}}$, i.e., a function from an arbitrary type to another arbitrary
type. We can easily derive inconsistency from this function:
applying it to $\top$ and $\bot$ yields a function of type $\top\to\bot$.
